\documentclass{resume} 
\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} 
\usepackage[hidelinks]{hyperref}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Khanh Le Vu}
\address{\href{https://www.linkedin.com/in/vulekhanh/}{linkedin.com/in/vulekhanh/} \\ \href{https://github.com/vulekhanh}{github.com/vulekhanh}}
\address{(+84)902568018 \\ vulekhanh69@gmail.com}
\address{Ho Chi Minh city, Vietnam} 
\begin{document}

\begin{rSection}{Education}

{\bf University of Information Technology - VNUHCM} \hfill {\em September 2020 - Now} 
\\ Bachelor of Science - Software Engineering.\hfill { Overall GPA: 8.12 }

\end{rSection}

\begin{rSection}{Objective}
 To work for an organization which provides me the opportunity to improve my skills and knowledge to grow along with the organization objective.
\end{rSection}

\begin{rSection}{Projects}
{\bf Car Sales Management \hfill{Oct 2022 - Feb 2023}}
\begin{itemize}
    \item Tools: Figma, Git, Visual Studio.
    \item Technologies used: .NET WPF, SQL Server.
    \item Role (Members: 4): Full-stack developer.
    \item Designed, built the user interface along with the database which stores all the required information from customers and employees. Dealers can also track their monthly or annual revenue to create appropriate business plan for the future. 
\end{itemize}


{\bf SVP - Digital Wallet \hfill{Oct 2022 - Feb 2023}}
\begin{itemize}
    \item Tools: Figma, Git, Vim.
    \item Languages: HTML, CSS, Javascript.
    \item Role (Members: 4): UI/UX designer and Front-end developer.
    \item Designed and built a user-friendly UI on website. Customers can easily interact with the website with ease regardless of ages. 
\end{itemize}

{\bf Library Management Application \hfill{Apr 2022 - Jun 2022}}
\begin{itemize}
    \item Technology used: React Native, Firebase, NoSQL.
    \item Role (Members: 3): UI designer, project manager.
    \item Designed and developed a simple, yet elegant user
    interface.
    \item Used clean code for easy and convenient future
    maintenance.    
\end{itemize}

{\bf Caro Game \hfill{Oct 2021 - Jan 2022}}
\begin{itemize}
    \item Technology used: .NET, SQL server, Photoshop.
    \item Role (Members: 2): UI and database designer.
    \item Designed and built a user-friendly UI.
    \item Created database that can store player's information
    including name, avatar, score, date.    
\end{itemize}


\end{rSection}

\begin{rSection}{Technical Strengths}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Languages \ & C, C++, Python, Java, Javascript, C\#  \\
Technologies & MVC, MVVM, HTML5, CSS, Latex\\
Frameworks/Libraries & React Native, Reactjs, .NET\\
Tools & Git, Travis CI, Jira, Docker, Linux, Vim, Jupyter Notebook \\
Databases & SQL, NoSQL\\
Cloud Technologies & Firebase\\
\end{tabular}

\end{rSection}

\begin{rSection}{Languages}

    \begin{tabular}{ @{} >{\bfseries}l @{\hspace{18ex}} l }
    English & Fluent  \\
    Vietnamese & Native\\
    French & Beginner\\
    \end{tabular}
    
    \end{rSection}
\end{document}